Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-04-14 parts/intro.tex
add internal refs to the new theorems in intro (additions compared to [12])

The main additions in this paper compared to \cite{FPMR13-CS2Bio} are
two theorems, the first
stating that any Process Hitting model with any number of classes of priorities can be represented
with only two classes of priorities,
and the other giving a method to cope with successive reachability.
Both aim at extending the application range of the static analysis we developed.

>>>>

The main additions in this paper compared to \cite{FPMR13-CS2Bio} are
%two theorems, the first
\pref{thm:ordered-ua} that gives a method to cope with successive reachability,
and %the second
\pref{th:bisimPHP} which states that any Process Hitting model with any number of classes of priorities
can be represented with only two classes of priorities.
Both aim at extending the application range of the static analysis we developed.
